Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and it's audio-description

### 2020-05-02 paper/main.tex
revise table of AO events

    \caption{Overview of events to build the 18 regressors for the analysis of the audio-only (AO) stimulus. Some of the original categories (female, females, fname; male, males, mname; face, head; see Table \ref{tab:descr-nouns}) were pooled into new categories (sex\_f; sex\_m; fahead)

@@

body & descr & \aoBodyAll & \aoBodyI & \aoBodyII & \aoBodyIII & \aoBodyIV & \aoBodyV & \aoBodyVI & \aoBodyVII & \aoBodyVIII \tabularnewline
bpart & descr & \aoBpartAll & \aoBpartI & \aoBpartII & \aoBpartIII & \aoBpartIV & \aoBpartV & \aoBpartVI & \aoBpartVII & \aoBpartVIII \tabularnewline
fahead & descr & \aoFaheadAll & \aoFaheadI & \aoFaheadII & \aoFaheadIII & \aoFaheadIV & \aoFaheadV & \aoFaheadVI & \aoFaheadVII & \aoFaheadVIII \tabularnewline
furn & descr & \aoFurnAll & \aoFurnI & \aoFurnII & \aoFurnIII & \aoFurnIV & \aoFurnV & \aoFurnVI & \aoFurnVII & \aoFurnVIII \tabularnewline
geo & descr & \aoGeoAll & \aoGeoI & \aoGeoII & \aoGeoIII & \aoGeoIV & \aoGeoV & \aoGeoVI & \aoGeoVII & \aoGeoVIII \tabularnewline
groom & descr & \aoGroomAll & \aoGroomI & \aoGroomII & \aoGroomIII & \aoGroomIV & \aoGroomV & \aoGroomVI & \aoGroomVII & \aoGroomVIII \tabularnewline
object & descr & \aoObjAll & \aoObjI & \aoObjII & \aoObjIII & \aoObjIV & \aoObjV & \aoObjVI & \aoObjVII & \aoObjVIII \tabularnewline
se\_new & descr & \aoSenewAll & \aoSenewI & \aoSenewII & \aoSenewIII & \aoSenewIV & \aoSenewV & \aoSenewVI & \aoSenewVII & \aoSenewVIII \tabularnewline
se\_old & descr & \aoSeoldAll & \aoSeoldI & \aoSeoldII & \aoSeoldIII & \aoSeoldIV & \aoSeoldV & \aoSeoldVI & \aoSeoldVII & \aoSeoldVIII \tabularnewline
sex\_f & descr & \aoSexfAll & \aoSexfI & \aoSexfII & \aoSexfIII & \aoSexfIV & \aoSexfV & \aoSexfVI & \aoSexfVII & \aoSexfVIII \tabularnewline
sex\_m & descr & \aoSexmAll & \aoSexmI & \aoSexmII & \aoSexmIII & \aoSexmIV & \aoSexmV & \aoSexmVI & \aoSexmVII & \aoSexmVIII \tabularnewline
sex\_u & descr & \aoSexuAll & \aoSexuI & \aoSexuII & \aoSexuIII & \aoSexuIV & \aoSexuV & \aoSexuVI & \aoSexuVII & \aoSexuVIII \tabularnewline

@@

vlo\_ch & descr & \aoVlochAll & \aoVlochI & \aoVlochII & \aoVlochIII & \aoVlochIV & 0 & \aoVlochV & \aoVlochVI & \aoVlochVII \tabularnewline
vno\_cut & descr & \aoVnocutAll & \aoVnocutI & \aoVnocutII & \aoVnocutIII & \aoVnocutIV & \aoVnocutV & \aoVnocutVI & \aoVnocutVII & \aoVnocutVIII \tabularnewline
vpe\_new & descr & \aoVpenewAll & \aoVpenewI & \aoVpenewII & \aoVpenewIII & \aoVpenewIV & \aoVpenewV & \aoVpenewVI & \aoVpenewVII & \aoVpenewVIII \tabularnewline

@@

vpe\_old & descr & \aoVpeoldAll & \aoVpeoldI & \aoVpeoldII & 0 & \aoVpeoldIII & \aoVpeoldIV & \aoVpeoldV & \aoVpeoldVI & \aoVpeoldVII \tabularnewline
vse\_new & descr & \aoVsenewAll & \aoVsenewI & \aoVsenewII & \aoVsenewIII & \aoVsenewIV & \aoVsenewV & \aoVsenewVI & \aoVsenewVII & \aoVsenewVIII \tabularnewline
vse\_old & descr & \aoVseoldAll & \aoVseoldI & \aoVseoldII & \aoVseoldIII & \aoVseoldIV & \aoVseoldV & \aoVseoldVI & \aoVseoldVII & \aoVseoldVIII \tabularnewline

@@

fg\_ad\_rms & root mean square & \aoFgadrmsAll & \aoFgadrmsI & \aoFgadrmsII & \aoFgadrmsIII & \aoFgadrmsIV & \aoFgadrmsV & \aoFgadrmsVI & \aoFgadrmsVII & \aoFgadrmsVIII \tabularnewline

@@

\begin{table*}
\caption{Regressors used in the analysis of the audio-description.}
\begin{tabular}{lll}
\toprule
\textbf{name} & \textbf{count} & \textbf{description} \\
\midrule
body & 66 & trunk of the body or overlaid clothes \\
bpart & 69 & limbs and trousers \\
facehead & 83 & face(parts) or head(parts) \\
furniture & 50 & big inventory of rooms (insides/outsides) \\
geo & 125 & immobile landmarks \\
geo-room & 105 & elements defining a locale's spatial layout \\
setting\_new & 86 & first-time mentioned setting \\
setting\_old & 37 & recurring setting \\
object & 284 & inanimate entities with firm boundaries \\
sex\_f & 108 & female person(s), name \\
sex\_m & 403 & male person(s), name \\
vse\_new & 96 & control for movie cuts; s. table y \\
vse\_old & 90 & control for movie cuts; s. table y \\
vloc\_change & 89 & control for movie cuts; s. table y \\
vpe\_new & 386 & control for movie cuts; s. table y \\
vpe\_old & 208 & control for movie cuts; s. table y \\
fg\_ad\_lrdiff & xx &  left-right volume difference \\
fg\_ad\_rms & xx & root mean square amplitude \\
\bottomrule
\end{tabular}
\end{table*}

>>>>

    \caption{Overview of events to build the 18 regressors for the analysis of the audio-only (AO) stimulus. Some of the original categories (female, females, fname; male, males, mname; face, head; object, objects; see Table \ref{tab:descr-nouns}) were pooled into new categories (sex\_f; sex\_m; fahead; object)

@@

body & trunk of the body or overlaid clothes & \aoBodyAll & \aoBodyI & \aoBodyII & \aoBodyIII & \aoBodyIV & \aoBodyV & \aoBodyVI & \aoBodyVII & \aoBodyVIII \tabularnewline
bpart & limbs and trousers & \aoBpartAll & \aoBpartI & \aoBpartII & \aoBpartIII & \aoBpartIV & \aoBpartV & \aoBpartVI & \aoBpartVII & \aoBpartVIII \tabularnewline
fahead & face(parts) or head(parts) & \aoFaheadAll & \aoFaheadI & \aoFaheadII & \aoFaheadIII & \aoFaheadIV & \aoFaheadV & \aoFaheadVI & \aoFaheadVII & \aoFaheadVIII \tabularnewline
furn & big inventory of rooms (insides/outsides) & \aoFurnAll & \aoFurnI & \aoFurnII & \aoFurnIII & \aoFurnIV & \aoFurnV & \aoFurnVI & \aoFurnVII & \aoFurnVIII \tabularnewline
geo & immobile landmarks & \aoGeoAll & \aoGeoI & \aoGeoII & \aoGeoIII & \aoGeoIV & \aoGeoV & \aoGeoVI & \aoGeoVII & \aoGeoVIII \tabularnewline
groom & elements defining a locale's spatial layout & \aoGroomAll & \aoGroomI & \aoGroomII & \aoGroomIII & \aoGroomIV & \aoGroomV & \aoGroomVI & \aoGroomVII & \aoGroomVIII \tabularnewline
object & inanimate entities with firm boundaries & \aoObjAll & \aoObjI & \aoObjII & \aoObjIII & \aoObjIV & \aoObjV & \aoObjVI & \aoObjVII & \aoObjVIII \tabularnewline
se\_new & first-time mentioned setting & \aoSenewAll & \aoSenewI & \aoSenewII & \aoSenewIII & \aoSenewIV & \aoSenewV & \aoSenewVI & \aoSenewVII & \aoSenewVIII \tabularnewline
se\_old & recurring setting & \aoSeoldAll & \aoSeoldI & \aoSeoldII & \aoSeoldIII & \aoSeoldIV & \aoSeoldV & \aoSeoldVI & \aoSeoldVII & \aoSeoldVIII \tabularnewline
sex\_f & female person(s), name & \aoSexfAll & \aoSexfI & \aoSexfII & \aoSexfIII & \aoSexfIV & \aoSexfV & \aoSexfVI & \aoSexfVII & \aoSexfVIII \tabularnewline
sex\_m & male person(s), name & \aoSexmAll & \aoSexmI & \aoSexmII & \aoSexmIII & \aoSexmIV & \aoSexmV & \aoSexmVI & \aoSexmVII & \aoSexmVIII \tabularnewline
sex\_u & person(s) of unknown sex & \aoSexuAll & \aoSexuI & \aoSexuII & \aoSexuIII & \aoSexuIV & \aoSexuV & \aoSexuVI & \aoSexuVII & \aoSexuVIII \tabularnewline

@@

vse\_new & control for movie cut & \aoVsenewAll & \aoVsenewI & \aoVsenewII & \aoVsenewIII & \aoVsenewIV & \aoVsenewV & \aoVsenewVI & \aoVsenewVII & \aoVsenewVIII \tabularnewline
vse\_old & control for movie cut & \aoVseoldAll & \aoVseoldI & \aoVseoldII & \aoVseoldIII & \aoVseoldIV & \aoVseoldV & \aoVseoldVI & \aoVseoldVII & \aoVseoldVIII \tabularnewline
vlo\_ch & control for movie cut & \aoVlochAll & \aoVlochI & \aoVlochII & \aoVlochIII & \aoVlochIV & 0 & \aoVlochV & \aoVlochVI & \aoVlochVII \tabularnewline
vpe\_new & control for movie cut & \aoVpenewAll & \aoVpenewI & \aoVpenewII & \aoVpenewIII & \aoVpenewIV & \aoVpenewV & \aoVpenewVI & \aoVpenewVII & \aoVpenewVIII \tabularnewline

@@

vpe\_old & control for movie cut & \aoVpeoldAll & \aoVpeoldI & \aoVpeoldII & 0 & \aoVpeoldIII & \aoVpeoldIV & \aoVpeoldV & \aoVpeoldVI & \aoVpeoldVII \tabularnewline

@@

fg\_ad\_rms & root mean square loudness & \aoFgadrmsAll & \aoFgadrmsI & \aoFgadrmsII & \aoFgadrmsIII & \aoFgadrmsIV & \aoFgadrmsV & \aoFgadrmsVI & \aoFgadrmsVII & \aoFgadrmsVIII \tabularnewline

@@
